---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
render_images <- function(path, plots) {
  paths <- file.path(path, plots)
  paste0('<a href="', paths, '">', 
         pander::pandoc.image.return(paths),
         '</a>')
}
us_path <- ifelse(grepl("results", getwd()), 
                   file.path("."), 
                   file.path("results", "us"))
black_path <- file.path(us_path, "black")
white_path <- file.path(us_path, "white")
```

_Updated: `r Sys.Date()`._


## Model

$$\left(x_i \left| \{ \mathbf{r}_i, \mathbf{p}_i\}, u_i\right.\right)
\sim {\rm Poisson}\left(\Lambda_{i,4}\left|\{\mathbf{r}_i,\mathbf{p}_i, u_i\}\right.\right)$$

$$\left(y_i \left| \{ \mathbf{r}_i, \mathbf{p}_i\}, u_i\right.\right)
\sim {\rm Poisson}\left(\Lambda_{i,3}\left|\{\mathbf{r}_i,\mathbf{p}_i, u_i\}\right.\right)$$

$$\left(w_i^{(\rm{obs})} \left| \{ \mathbf{r}_i, p_i^{(1)}, u_i\} \right.\right)
\sim {\rm Poisson}\left(w_{i}\right)$$

where $w_{i}= p_{i}^{(1)}\cdot \sum_{j=1}^{i-1} \{r_{j}^{(1)} \cdot \left(1 - u_{j}\right)\} + r_i^{(2)}$ and $w_{i}^{({\rm obs})} = p_{i}^{(1, {\rm obs})}\cdot\sum_{j=1}^{i-1} \{r_{j}^{(1,{\rm obs})} \cdot \left(1 - u_{j}\right)\} + r_i^{(2, {\rm obs})}$

## Priors

$$\delta_i^{(1)}\sim N\left(\delta_{i-1}^{(1)}, \sigma_\delta^2\right),$$
$$\delta_i^{(2)}\sim N\left(\delta_{i-1}^{(2)}, \sigma_\delta^2\right),$$ 
and
$$\delta_i^{(3)}\sim N\left(\delta_{i-1}^{(3)}, \sigma_\delta^2\right)$$ 

where $\delta_0^{(1)}=\rm{logit}\left(0.015\right)$, $\delta_0^{(2)}=\rm{logit}\left(0.01\right)$, $\delta_0^{(1)}=\rm{logit}\left(0.0005\right)$, 
and $\sigma_\delta=\lvert\sigma_\delta'\rvert$, $\sigma_\delta'\sim\left(0, 1\right)$


$$\gamma_i^{(1)}\sim N\left(\gamma_{i-1}^{(1)}, \sigma_\gamma^2\right)$$ 
and
$$\gamma_i^{(2)}\sim N\left(\gamma_{i-1}^{(2)}, \sigma_\gamma^2\right)$$ 

where $\gamma_0^{(1)}=\log\left(0.1 \cdot m_0\right)$, $\gamma_0^{(2)}=\log\left(0.00015 \cdot m_0\right)$, and $\sigma_\gamma=\lvert\sigma_\gamma'\rvert$, $\sigma_\gamma'\sim (0, 1)$

$$\phi_1\sim N\left(0, 1\right)\text{ and }\phi_2\sim N\left(0, 1\right)$$

$u_i$ for $i=1,\ldots,5$ represent annual crude mortality rates among the respective population and $m_0$ is the general population size at time 0.

Assumptions:

+  $r_0^{(1)}$ is approximately 10% of the population
+  $r_0^{(2)}$ is approximately 0.15 per thousand population
+  with a high level of uncertainty (weakly informative)

## Results

```{r include=FALSE}
plot_names <- dir(black_path)
diagnostic_plots <- plot_names[grepl("^00-diagnostics", plot_names)]
wxy_plots <- plot_names[grepl("^02-.+[w|x|y].png", plot_names)][c(1, 3, 2)]
p_plots <- plot_names[grepl("^02-.+p\\d.png", plot_names)]
r_plots <- plot_names[grepl("^02-.+r\\d.png", plot_names)]
init_logitp_plots <- plot_names[grepl("^01-.+logitp.png", plot_names)]
sigma_plots <- plot_names[grepl("^01-.+sig.+.png", plot_names)]
phi_plots <- plot_names[grepl("^01-.+phi\\d.png", plot_names)]
```

### Incidences

+  Curves on the left margin indicate prior distributions where available.
+  Connected solid diamonds indicate posterior medians with 80% and 95% credible intervals indicated with vertical lines.

```{r}
knitr::kable(
  rbind(
    `Non-Hispanic black` = render_images(black_path, r_plots),
    `Non-Hispanic white` = render_images(white_path, r_plots)
  ), 
  col.names = c("r1", "r2"),
  row.names = TRUE
)
```

### Transition probabilities

+  Curves on the left margin indicate prior distributions where available.
+  Connected solid diamonds indicate posterior medians with 80% and 95% credible intervals indicated with vertical lines.
+  White diamonds indicate the ratio estimates.

```{r}
knitr::kable(
  rbind(
    `Non-Hispanic black` = render_images(black_path, p_plots),
    `Non-Hispanic white` = render_images(white_path, p_plots)
  ), 
  col.names = c("p1", "p2", "p3"),
  row.names = TRUE
)
```

### Observed counts

+  Connected solid diamonds indicate posterior medians with 80% and 95% credible intervals indicated with vertical lines.
+  Crosses indicate the observed counts.

```{r}
knitr::kable(
  rbind(
    `Non-Hispanic black` = render_images(black_path, wxy_plots),
    `Non-Hispanic white` = render_images(white_path, wxy_plots)
  ), 
  col.names = c("W", "Y", "X"),
  row.names = TRUE
)
```

### Hyperparameters

### Initial prevalences

+  The values represent logit-transformed proportion of the general subpopulation.

```{r}
knitr::kable(
  rbind(
    `Non-Hispanic black` = render_images(black_path, init_logitp_plots),
    `Non-Hispanic white` = render_images(white_path, init_logitp_plots)
  ), 
  col.names = c("State 1", "State 2"),
  row.names = TRUE
)
```

### Random walk standard deviations

```{r}
knitr::kable(
  rbind(
    `Non-Hispanic black` = render_images(black_path, sigma_plots),
    `Non-Hispanic white` = render_images(white_path, sigma_plots)
  ), 
  col.names = c("$\\sigma_\\delta$", "$\\sigma_\\gamma$"),
  row.names = TRUE, escape = FALSE
)
```

### Bias adjustment terms

```{r}
knitr::kable(
  rbind(
    `Non-Hispanic black` = render_images(black_path, phi_plots),
    `Non-Hispanic white` = render_images(white_path, phi_plots)
  ), 
  col.names = c("$\\phi_1$", "$\\phi_2$"),
  row.names = TRUE, escape = FALSE
)
```

## Diagnostic plots

Several diagnostic plots are available in subdirectories for [the non-Hispanic black model](black/) and [the non-Hispanic white model](white/).
