---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

sim_path <- ifelse(grepl("results", getwd()), 
                   file.path("."), 
                   file.path("results", "sim"))
fit_no_ratio_path <- file.path(sim_path, "no-ratio-estimate")
fit_ratio_path <- file.path(sim_path, "ratio-estimate")
render_images <- function(path, plots) {
  paths <- file.path(path, plots)
  paste0('<a href="', paths, '">', 
         pander::pandoc.image.return(paths),
         '</a>')
}
```

_Updated: `r Sys.Date()`._

## Simulation parameters

```{r}
load(file.path(
  ifelse(grepl("results", getwd()),
         file.path("..", ".."),
         file.path(".")),
  "data", "sim", "params.RData"
))
knitr::kable(
  cbind(
    c("n", "$r_0^{\\rm TRUE}$", "$p_0^{\\rm TRUE}$", "$\\sigma_\\gamma^{\\rm TRUE}$", "$\\sigma_\\delta^{\\rm TRUE}$", "u"),
    c(n, paste(r0, collapse = ", "), paste(p0, collapse = ", "),
      siggamma, sigdelta, u)
  ),
  escape = FALSE,
  col.names = c("Parameter", "Value")
)
```

## Simulated data

### Incidences

```{r}
sim_plots <- dir(sim_path)[grep(".png", dir(sim_path))]
sim_r_plots <- sim_plots[grepl("^r\\d", sim_plots)]
knitr::kable(
  t(render_images(sim_path, sim_r_plots)), 
  col.names = c("r1", "r2")
)
```

### Transition probabilities

```{r}
sim_p_plots <- sim_plots[grepl("^p\\d", sim_plots)]
knitr::kable(
  t(render_images(sim_path, sim_p_plots)), 
  col.names = c("p1", "p2", "p3")
)
```

## Observed counts

```{r}
sim_wxy_plots <- sim_plots[grepl("[a-z]\\.", sim_plots)][c(1,3,2)]
knitr::kable(
  t(render_images(sim_path, sim_wxy_plots)), 
  col.names = c("W", "Y", "X")
)
```

## Fitting with matching priors

### Priors

+  Normal for $\gamma_0 =\log\left(r_0\right)$ such that their means are $\log\left(r_0^{\rm TRUE}\right)$ with standard deviations following a half normal distribution with $\sigma=1$.
+  Normal for $\delta_0 ={\rm logit}\left(p_0\right)$ such that their means are ${\rm logit}\left(p_0^{\rm TRUE}\right)$ with standard deviations following a half normal distribution with $\sigma=1$.


### Results

### Incidences

+  Curves on the left margin indicate prior distributions where available.
+  Connected solid diamonds indicate posterior medians with 80% and 95% credible intervals indicated with vertical lines.
+  White diamonds indicate the simulated true values.

```{r}
fit_no_ratio_plots <- dir(fit_no_ratio_path)[grep(
  ".png", dir(fit_no_ratio_path))]
fit_ratio_plots <- dir(fit_ratio_path)[grep(
  ".png", dir(fit_ratio_path))]
fit_no_ratio_r_plots <- fit_no_ratio_plots[grepl(
  "^01-.+r\\d.png", fit_no_ratio_plots)]
fit_ratio_r_plots <- fit_ratio_plots[grepl(
  "^01-.+r\\d.png", fit_ratio_plots)]
knitr::kable(
  rbind(
    `Without ratio estimates` = render_images(
      fit_no_ratio_path, fit_no_ratio_r_plots),
    `With ratio estimates` = render_images(
      fit_ratio_path, fit_ratio_r_plots)
  ), 
  col.names = c("r1", "r2"),
  row.names = TRUE
)
```

### Transition probabilities

+  Curves on the left margin indicate prior distributions where available.
+  Connected solid diamonds indicate posterior medians with 80% and 95% credible intervals indicated with vertical lines.
+  White diamonds indicate the simulated true values.
+  Grey diamonds indicate the simulated ratio estimates.

```{r}
fit_no_ratio_p_plots <- fit_no_ratio_plots[grepl(
  "^01-.+p\\d.png", fit_no_ratio_plots)]
fit_ratio_p_plots <- fit_ratio_plots[grepl(
  "^01-.+p\\d.png", fit_ratio_plots)]
knitr::kable(
  rbind(
    `Without ratio estimates` = render_images(
      fit_no_ratio_path, fit_no_ratio_p_plots),
    `With ratio estimates` = render_images(
      fit_ratio_path, fit_ratio_p_plots)
  ), 
  col.names = c("p1", "p2", "p3"),
  row.names = TRUE
)
```

### Observed counts

+  Connected solid diamonds indicate posterior medians with 80% and 95% credible intervals indicated with vertical lines for the means.
+  White diamonds indicate the simulated observed counts.

```{r}
fit_no_ratio_wxy_plots <- fit_no_ratio_plots[grepl(
  "^01-.+[w|x|y|].png", fit_no_ratio_plots)][c(1, 3, 2)]
fit_ratio_wxy_plots <- fit_ratio_plots[grepl(
  "^01-.+[w|x|y].png", fit_ratio_plots)][c(1, 3, 2)]
knitr::kable(
  rbind(
    `Without ratio estimates` = render_images(
      fit_no_ratio_path, fit_no_ratio_wxy_plots),
    `With ratio estimates` = render_images(
      fit_ratio_path, fit_ratio_wxy_plots)
  ), 
  col.names = c("W", "Y", "X"),
  row.names = TRUE
)
```

## Diagnostic plots

Several diagnostic plots are available in subdirectories for [the model without ratio estimates](no-ratio-estimate/) and [the model with ratio estimates](ratio-estimate/).
